HO unification from object language to meta language

### 2024-02-06 main.tex
update tex

This small set of instance thanks a first phase of class and instance\todo{explain compilation of pred and inst?}
compilation is translated into the following \elpi program:

\begin{mintedTcolorbox}{elpi}
  type XXX Args .. -> term -> o.
  XXX Args ... (ZZZ P1 ... PN) :-
    premese...
  WWW Args ... (ZZZ P1 ... PN) :-
    premese...
\end{mintedTcolorbox}

Type-class resolution starts from a query, that is a class applied to some
argument. This \coq term is translated into a term of the meta language and the
search for a solution in the database is started. However, since unification is
performed on the head of the clause, it may happen that the term representation
in the meta language is not sufficiently powerful to understand that two terms
unifying in the object language should also unify in the meta language.

@@

Without any loss of generality, in \cref{table:coq2elpi} we present a subset of
the terms in the object language and for each term we give its representation in
the meta language.

>>>>

This small set of instances after a first phase of\todo{explain compilation of pred and inst?}
compilation is translated into the following \elpi rules:

\begin{mintedTcolorbox}{elpi}
  type XXX Args .. -> term -> o.
  XXX Args ... (WWW P1 ... PN) :-
    premese...
  XXX Args ... (ZZZ P1 ... PN) :-
    premese...
\end{mintedTcolorbox}

Type-class resolution starts from a query, that is a class applied to some
argument. This \coq term is translated into a term of the meta language and the
search for a solution in the database is started. However, since unification is
performed on the head of the clause, it may happen that the term representation
in the meta language may hide some unification properties that are true in the
object language.

@@

Without any loss of generality, in \cref{table:coq2elpi} we present a subset of
the terms in the object language and for each term we give its representation in
the meta language. This encoding is enough to fall into unification problems.
For example, rules like

\begin{center}
  \elpiIn{p (lam x\ (app F x)) :- ... F ...}
\end{center}

cannot unify with goals like

\begin{center}
  \elpiIn{p (lam x\ app (app (const "f") x) x).}
\end{center}

Since \elpiIn{F} does not see \elpiIn{x} even though it is applied to \elpiIn{x}
in the object language.
